A demonstration of the \LaTeXe\ class file for \itshape{\journalnamelc}\footnotemark[2]

### 2019-10-01 journal/relatedwork.tex
typo

Metallaxis \cite{Metallaxis,MetalSelect,Papadakis}, in contrast to MUSE/MUSEUM (and our own work), relies on the idea that mutants that are (relative to other killed mutants) mostly killed by failing tests likely have a connection to a program defect or defects.  This idea relies on a fundamentally different notion of ``killing'' a mutant than the one primarily used in this paper.  We generally speak of a mutant being killed when the mutant makes a previously passing test fail; in this sense, a failing test cannot kill a mutant.  However, these ``correctness kills'' are not the only possible notion of mutant kill used in the literature; a different approach is to consider a mutant killed whenever it produces a different output than the original program.  This point of view, unfortunately, is not obviously useful for compiler mutants, where almost all mutants, however benign, of covered code, will result in some (perhaps meaningless) change in the output binary.  We have therefore consider a mutant killed only when it causes semantically wrong output from a compiled program, a fairly complex specification-based notion of difference.  Compilers may therefore be an unusually poor fit for the Metallaxis approach, which, as our results above show, is quite competitive for more ``normal'' localization, where output (vs. specification-satisfaction/correctness) differences are likely to be meaningful.  Extending our approach beyond ``correctness kills'' (at least for non-compiler contexts) is an interesting possible line of future research.

>>>>

Metallaxis \cite{Metallaxis,MetalSelect,Papadakis}, in contrast to MUSE/MUSEUM (and our own work), relies on the idea that mutants that are (relative to other killed mutants) mostly killed by failing tests likely have a connection to a program defect or defects.  This idea relies on a fundamentally different notion of ``killing'' a mutant than the one primarily used in this paper.  We generally speak of a mutant being killed when the mutant makes a previously passing test fail; in this sense, a failing test cannot kill a mutant.  However, these ``correctness kills'' are not the only possible notion of mutant kill used in the literature; a different approach is to consider a mutant killed whenever it produces a different output than the original program.  This point of view, unfortunately, is not obviously useful for compiler mutants, where almost all mutants, however benign, of covered code, will result in some (perhaps meaningless) change in the output binary.  We have therefore considered a mutant killed only when it causes semantically wrong output from a compiled program, a fairly complex specification-based notion of difference.  Compilers may therefore be an unusually poor fit for the Metallaxis approach, which, as our results above show, is quite competitive for more ``normal'' localization, where output (vs. specification-satisfaction/correctness) differences are likely to be meaningful.  Extending our approach beyond ``correctness kills'' (at least for non-compiler contexts) is an interesting possible line of future research.
